---
title: "Study 1: Extra (not reported)"
subtitle: "Luhrmann, Weisman, et al."
output: 
  html_notebook:
    theme: flatly
    toc: true
    toc_float: true
---

In this notebook, we conduct additional analyses for Study 1: In-depth interviews with people of faith (not reported in the main text or the Supplemental Information of the paper).

```{r}
source("../../scripts_general/dependencies.R")
source("../../scripts_general/custom_funs.R")
source("../../scripts_general/var_recode_contrast.R")
source("../scripts_s1/s1_var_groups.R")
source("../../scripts_general/data_load.R")
```


# More on recoding ("QTS2")

```{r}
d1r_byquestion <- read_csv("../data/study1r_byquestion.csv")
```

```{r}
d1r <- read_csv("../data/study1r.csv") %>%
  rename_at(vars(contains("score")), funs(gsub("score", "recoded", .))) %>%
  full_join(d1) %>%
  mutate(country = factor(country, levels = levels_country),
         site = factor(site, levels = levels_site),
         religion = factor(religion, levels = levels_religion),
         researcher = factor(researcher, levels = levels_researcher))

contrasts(d1r$country) <- contrasts_country
contrasts(d1r$site) <- contrasts_site
contrasts(d1r$religion) <- contrasts_religion
```

## Averages, by score

```{r}
d1r %>% 
  select(country, subject_id, ends_with("recoded"), ends_with("score")) %>%
  gather(scale, score, -c(country, subject_id)) %>%
  filter(grepl("spirit", scale) | grepl("other", scale)) %>%
  mutate(score_type = case_when(grepl("recoded", scale) ~ "recoded",
                                grepl("score", scale) ~ "original",
                                TRUE ~ NA_character_),
         score_type = factor(score_type, levels = c("original", "recoded")),
         scale = case_when(grepl("spirit", scale) ~ "spiritual experiences",
                           grepl("other", scale) ~ "other extraordinary experiences",
                           TRUE ~ NA_character_),
         scale = factor(scale, levels = c("spiritual experiences", 
                                          "other extraordinary experiences"))) %>%
  ggplot(aes(x = scale, y = score, group = score_type)) +
  # geom_point(aes(color = score_type), alpha = 0.2,
  #            position = position_jitterdodge(jitter.width = 0.1,
  #                                            dodge.width = 0.5,
  #                                            jitter.height = 0.04)) +
  geom_pointrange(data = . %>%
                    group_by(scale, score_type) %>%
                    langcog::multi_boot_standard(col = "score", na.rm = T),
                  aes(y = mean, ymin = ci_lower, ymax = ci_upper, fill = score_type),
                  position = position_dodge(width = 0.5),
                  shape = 21, fatten = 6) +
  labs(title = "Comparing recoded scores (QTS2) to original scores (QTS1)",
       x = "Scale", y = "Score (range: 0-1)",
       fill = "Score type")
```

```{r}
lmer(score ~ score_type * scale + (1 | subject_id), 
   data = d1r %>% 
     select(country, subject_id, ends_with("recoded"), ends_with("score")) %>%
     gather(scale, score, -c(country, subject_id)) %>%
     filter(grepl("spirit", scale) | grepl("other", scale)) %>%
     mutate(score_type = case_when(grepl("recoded", scale) ~ "recoded",
                                   grepl("score", scale) ~ "original",
                                   TRUE ~ NA_character_),
            score_type = factor(score_type, levels = c("original", "recoded")),
            scale = case_when(grepl("spirit", scale) ~ "spiritual experiences",
                              grepl("other", scale) ~ "other extraordinary experiences",
                              TRUE ~ NA_character_),
            scale = factor(scale, levels = c("spiritual experiences", 
                                             "other extraordinary experiences"))),
   contrasts = list(score_type = "contr.sum", scale = "contr.sum")) %>%
  summary()
```

```{r}
d1r %>% 
  select(country, subject_id, ends_with("recoded"), ends_with("score")) %>%
  gather(scale, score, -c(country, subject_id)) %>%
  filter(grepl("spirit", scale) | grepl("other", scale)) %>%
  mutate(score_type = case_when(grepl("recoded", scale) ~ "recoded",
                                grepl("score", scale) ~ "original",
                                TRUE ~ NA_character_),
         score_type = factor(score_type, levels = c("original", "recoded")),
         scale = case_when(grepl("spirit", scale) ~ "spiritual exp.",
                           grepl("other", scale) ~ "other exp.",
                           TRUE ~ NA_character_),
         scale = factor(scale, levels = c("spiritual exp.", 
                                          "other exp."))) %>%
  ggplot(aes(x = scale, y = score, group = score_type)) +
  facet_grid(~ country) +
  # geom_point(aes(color = score_type), alpha = 0.2,
  #            position = position_jitterdodge(jitter.width = 0.1,
  #                                            dodge.width = 0.5,
  #                                            jitter.height = 0.04)) +
  geom_pointrange(data = . %>%
                    group_by(scale, score_type, country) %>%
                    langcog::multi_boot_standard(col = "score", na.rm = T),
                  aes(y = mean, ymin = ci_lower, ymax = ci_upper, fill = score_type),
                  position = position_dodge(width = 0.5),
                  shape = 21, fatten = 6) +
  labs(title = "Comparing recoded scores (QTS2) to original scores (QTS1)",
       x = "Scale", y = "Score (range: 0-1)",
       fill = "Score type") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))
```

```{r, fig.width = 6, fig.asp = 0.8}
d1r %>% 
  select(country, site, religion, subject_id, 
         ends_with("recoded"), ends_with("score")) %>%
  gather(scale, score, -c(country, site, religion, subject_id)) %>%
  filter(grepl("spirit", scale) | grepl("other", scale)) %>%
  mutate(score_type = case_when(grepl("recoded", scale) ~ "recoded",
                                grepl("score", scale) ~ "original",
                                TRUE ~ NA_character_),
         score_type = factor(score_type, levels = c("original", "recoded")),
         scale = case_when(grepl("spirit", scale) ~ "spiritual exp.",
                           grepl("other", scale) ~ "other exp.",
                           TRUE ~ NA_character_),
         scale = factor(scale, levels = c("spiritual exp.", 
                                          "other exp."))) %>%
  ggplot(aes(x = scale, y = score, group = score_type)) +
  facet_grid(rows = vars(site, religion), cols = vars(country)) +
  geom_point(aes(color = score_type), alpha = 0.2,
             position = position_jitterdodge(jitter.width = 0.1,
                                             dodge.width = 0.5,
                                             jitter.height = 0.04)) +
  geom_pointrange(data = . %>%
                    group_by(scale, score_type, country, site, religion) %>%
                    langcog::multi_boot_standard(col = "score", na.rm = T),
                  aes(y = mean, ymin = ci_lower, ymax = ci_upper, fill = score_type),
                  position = position_dodge(width = 0.5),
                  shape = 21, fatten = 6) +
  labs(title = "Comparing recoded scores (QTS2) to original scores (QTS1)",
       x = "Scale", y = "Score (range: 0-1)",
       fill = "Score type", color = "Score type") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))
```

```{r}
d1r %>% 
  select(country, subject_id, coder, ends_with("recoded")) %>%
  gather(scale, score, -c(country, subject_id, coder)) %>%
  mutate(score_type = case_when(grepl("recoded", scale) ~ "recoded",
                                grepl("score", scale) ~ "original",
                                TRUE ~ NA_character_),
         score_type = factor(score_type, levels = c("original", "recoded")),
         scale = case_when(grepl("spirit", scale) ~ "spiritual exp.",
                           grepl("other", scale) ~ "other exp.",
                           TRUE ~ NA_character_),
         scale = factor(scale, levels = c("spiritual exp.", 
                                          "other exp."))) %>%
  filter(grepl("spirit", scale) | grepl("other", scale)) %>%
  ggplot(aes(x = scale, y = score, group = coder)) +
  facet_grid(~ country) +
  geom_point(aes(color = coder), alpha = 0.2,
             position = position_jitterdodge(jitter.width = 0.1,
                                             dodge.width = 0.5,
                                             jitter.height = 0.04)) +
  geom_pointrange(data = . %>%
                    group_by(scale, coder, country) %>%
                    langcog::multi_boot_standard(col = "score", na.rm = T),
                  aes(y = mean, ymin = ci_lower, ymax = ci_upper, fill = coder),
                  shape = 21, fatten = 5,
                  position = position_dodge(width = 0.5)) +
  labs(title = "Comparing coders in recoded dataset (QTS2)",
       x = "Scale", y = "Score (range: 0-1)", fill = "Coder", color = "Coder") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))
```

```{r}
lmer(score ~ scale * coder + (1 | subject_id), 
   data = d1r %>% 
     select(country, coder, subject_id, ends_with("recoded")) %>%
     distinct() %>%
     gather(scale, score, -c(country, subject_id, coder)) %>%
     filter(grepl("spirit", scale) | grepl("other", scale)) %>%
     mutate(scale = case_when(grepl("spirit", scale) ~ "spiritual experiences",
                              grepl("other", scale) ~ "other extraordinary experiences",
                              TRUE ~ NA_character_),
            scale = factor(scale, levels = c("spiritual experiences", 
                                             "other extraordinary experiences")),
            coder = factor(coder, levels = c("Nikki", "Maria", "Lucy"))),
   contrasts = list(scale = "contr.sum", 
                    coder = cbind("_NvGM" = c(1, 0, -1),
                                  "_MvGM" = c(0, 1, -1)))) %>%
  summary()
```

```{r, fig.width = 6, fig.asp = 0.8}
d1r %>% 
  select(country, site, religion, subject_id, coder, ends_with("recoded")) %>%
  gather(scale, score, -c(country, site, religion, subject_id, coder)) %>%
  mutate(score_type = case_when(grepl("recoded", scale) ~ "recoded",
                                grepl("score", scale) ~ "original",
                                TRUE ~ NA_character_),
         score_type = factor(score_type, levels = c("original", "recoded")),
         scale = case_when(grepl("spirit", scale) ~ "spiritual exp.",
                           grepl("other", scale) ~ "other exp.",
                           TRUE ~ NA_character_),
         scale = factor(scale, levels = c("spiritual exp.", 
                                          "other exp."))) %>%
  filter(grepl("spirit", scale) | grepl("other", scale)) %>%
  ggplot(aes(x = scale, y = score, group = coder)) +
  facet_grid(rows = vars(site, religion), cols = vars(country)) +
  geom_point(aes(color = coder), alpha = 0.2,
             position = position_jitterdodge(jitter.width = 0.1,
                                             dodge.width = 0.5,
                                             jitter.height = 0.04)) +
  geom_pointrange(data = . %>%
                    group_by(scale, coder, country, site, religion) %>%
                    langcog::multi_boot_standard(col = "score", na.rm = T),
                  aes(y = mean, ymin = ci_lower, ymax = ci_upper, fill = coder),
                  shape = 21, fatten = 5,
                  position = position_dodge(width = 0.5)) +
  geom_text(data = . %>% count(country, site, religion, coder, scale),
             aes(y = 0, label = paste0("n=", n), color = coder), 
            position = position_dodge(width = 1)) +
  labs(title = "Comparing coders in recoded dataset (QTS2)",
       x = "Scale", y = "Score (range: 0-1)", fill = "Coder", color = "Coder") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))
```



## Averages, by question

```{r, fig.width = 6, fig.asp = 0.4}
d1r_byquestion %>% 
  select(country, site, religion, subject_id, 
         !!s1_var_spirit, !!s1_var_other) %>%
  gather(question, recoded, -c(country, site, religion, subject_id)) %>%
  full_join(d1_byquestion %>%
              select(country, site, religion, subject_id, 
                     !!s1_var_spirit, !!s1_var_other) %>%
              gather(question, original, -c(country, site, religion, subject_id))) %>%
  gather(response_type, response, c(original, recoded)) %>%
  mutate(question = factor(question, levels = c(s1_var_spirit, s1_var_other)),
         response_type = factor(response_type, levels = c("original", "recoded"))) %>%
  ggplot(aes(x = question, y = response, group = response_type)) +
  geom_pointrange(data = . %>%
                    group_by(question, response_type) %>%
                    langcog::multi_boot_standard(col = "response", na.rm = T),
                  aes(y = mean, ymin = ci_lower, ymax = ci_upper,
                      fill = response_type),
                  position = position_dodge(width = 0.5),
                  shape = 21, fatten = 6) +
  labs(title = "Comparing recoded scores (QTS2) to original scores (QTS1)",
       x = "Question", y = "Response (range: 0-1)",
       fill = "Response type") +
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))
```

```{r}
d1r_byquestion %>% 
  select(country, site, religion, subject_id, 
         !!s1_var_spirit, !!s1_var_other) %>%
  gather(question, recoded, -c(country, site, religion, subject_id)) %>%
  full_join(d1_byquestion %>%
              select(country, site, religion, subject_id, 
                     !!s1_var_spirit, !!s1_var_other) %>%
              gather(question, original, -c(country, site, religion, subject_id))) %>%
  gather(response_type, response, c(original, recoded)) %>%
  mutate(question = factor(question, levels = c(s1_var_spirit, s1_var_other)),
         response_type = factor(response_type, levels = c("original", "recoded"))) %>%
  filter(question == "seehearnotgod") %>%
  count(response_type, response) %>%
  spread(response, n)
```

```{r}
d1r_byquestion %>% 
  select(country, site, religion, subject_id, 
         !!s1_var_spirit, !!s1_var_other) %>%
  gather(question, recoded, -c(country, site, religion, subject_id)) %>%
  full_join(d1_byquestion %>%
              select(country, site, religion, subject_id, 
                     !!s1_var_spirit, !!s1_var_other) %>%
              gather(question, original, -c(country, site, religion, subject_id))) %>%
  mutate(question = factor(question, levels = c(s1_var_spirit, s1_var_other))) %>%
  filter(question == "seehearnotgod") %>%
  mutate(match = (original == recoded)) %>%
  count(match) %>%
  mutate(prop = n/sum(n))
```




# Comparing first question to interviewer judgments when available

```{r}
d1_check_questions <- c("godvoxaloud", "godviavisions", "godviatouch", 
                        "godviasmell", "neartangiblegod", "presencenotgod", 
                        "presencedemon", "beingentbody", "seehearnotgod", 
                        "whitelight", "spiritbeingencounter", "voxwhenalone", 
                        "seethingscornereye")
```

```{r}
d1_check <- d1_byquestion %>% 
  select(country, subject_id, ends_with("_judge")) %>%
  gather(question, judgment, -c(country, subject_id)) %>%
  mutate(question = gsub("_judge", "", question)) %>%
  full_join(d1_byquestion %>% 
              select(country, subject_id, !!d1_check_questions) %>%
              gather(question, response, -c(country, subject_id)))

```

```{r}
d1_check %>%
  filter(question %in% d1_check_questions) %>%
  mutate(agree = (judgment == response),
         agree = ifelse(is.na(agree), 0, agree)) %>%
  group_by(question) %>%
  summarise(percent_agree = mean(agree, na.rm = T)) %>%
  arrange(percent_agree)
```

```{r}
s1_check_icc_df <- data.frame(question = character(), icc = numeric())
for(i in d1_check_questions){
  temp_icc <- icc_fun(d1_check, var_name = i, 
                      var1 = "judgment", var2 = "response")
  temp_res <- data.frame(question = i, icc = temp_icc)
  s1_check_icc_df <- full_join(s1_check_icc_df, temp_res)
  rm(temp_res, i)
}

s1_check_icc_df <- s1_check_icc_df %>%
  mutate(question = factor(question, levels = d1_check_questions),
         reliability = case_when(icc < 0.5 ~ "poor",
                                 icc < 0.75 ~ "moderate",
                                 icc < 0.9 ~ "good", 
                                 icc <= 1 ~ "excellent",
                                 TRUE ~ NA_character_),
         reliability = factor(reliability, 
                              levels = c("poor", "moderate", 
                                         "good", "excellent")),
         scale = case_when(question %in% s1_var_spirit ~ "spiritual experiences",
                           question %in% s1_var_other ~ "other experiences",
                           TRUE ~ NA_character_),
         scale = factor(scale, 
                        levels = c("spiritual experiences", "other experiences")))
```

```{r}
s1_check_icc_df %>% arrange(icc)
s1_check_icc_df %>% 
  mutate(scale = recode_factor(scale,
                               "spiritual experiences" = "spiritual",
                               "other experiences" = "other")) %>%
  ggplot(aes(x = question, y = icc, color = reliability)) + 
  facet_grid(~ scale, scales = "free", space = "free") +
  geom_point() +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
  scale_color_brewer(palette = "RdYlGn", direction = 1, drop = F) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1,
                                   color = ifelse(s1_check_icc_df$reliability == "poor",
                                                  "#d7191c", "black"))) +
  labs(title = "Comparing initial responses vs. later 'judgments'",
       x = "Question", y = "Intraclass correlation coefficient (ICC)")
```


# Percent with particular experiences

```{r}
d1_byquestion %>% 
  count(godvoxaloud) %>% 
  mutate(godvoxaloud = recode_factor(godvoxaloud, 
                                     "0" = "no", "0.5" = "maybe", "1" = "yes"),
         proportion = round(n/sum(n), 2))
```

```{r}
d1_byquestion %>% 
  filter(!is.na(godvoxaloud)) %>%
  count(country, godvoxaloud) %>% 
  mutate(godvoxaloud = recode_factor(godvoxaloud, 
                                     "0" = "no", "0.5" = "maybe", "1" = "yes")) %>%
  complete(country, nesting(godvoxaloud), fill = list(n = 0)) %>%
  spread(godvoxaloud, n) %>%
  mutate(total = no + maybe + yes) %>%
  janitor::adorn_totals() %>%
  mutate_at(vars(no, maybe, yes), funs(round(./total, 2)*100)) %>%
  select(-total) %>%
  data.frame() %>%
  mutate_at(vars(no, maybe, yes), funs(paste0(., "%"))) %>%
  kable() %>%
  kable_styling() %>%
  row_spec(6, bold = T)
```

```{r}
d1_byquestion %>% 
  filter(!is.na(godviavisions)) %>%
  count(country, godviavisions) %>% 
  mutate(godviavisions = recode_factor(godviavisions, 
                                       "0" = "no", "0.5" = "maybe", "1" = "yes")) %>%
  complete(country, nesting(godviavisions), fill = list(n = 0)) %>%
  spread(godviavisions, n) %>%
  mutate(total = no + maybe + yes) %>%
  janitor::adorn_totals() %>%
  mutate_at(vars(no, maybe, yes), funs(round(./total, 2)*100)) %>%
  select(-total) %>%
  data.frame() %>%
  mutate_at(vars(no, maybe, yes), funs(paste0(., "%"))) %>%
  kable() %>%
  kable_styling() %>%
  row_spec(6, bold = T)
```


# TML's additional analyses

## Focus on `godvoxaloud` and `godviavisions`

```{r}
d1_tml1 <- d1 %>% select(country, subject_id, abs_score, por_score) %>%
  full_join(d1_byquestion %>% 
              select(country, subject_id, godvoxaloud, godviavisions) %>%
              gather(question, response, -c(country, subject_id)) %>%
              mutate(response_yn = case_when(response < 1 ~ 0,
                                             response == 1 ~ 1,
                                             TRUE ~ NA_real_)))
```

```{r}
glmer(response_yn ~ scale(por_score) + (1 | question) + (1 | country), 
      family = "binomial", d1_tml1) %>% summary()
```

```{r}
glmer(response_yn ~ scale(abs_score) + (1 | question) + (1 | country), 
      family = "binomial", d1_tml1) %>% summary()
```

```{r}
glmer(response_yn ~ scale(por_score) + (1 | country), 
      family = "binomial", d1_tml1 %>% filter(question == "godvoxaloud")) %>% 
  summary()
```

```{r}
glmer(response_yn ~ scale(abs_score) + (1 | country), 
      family = "binomial", d1_tml1 %>% filter(question == "godvoxaloud")) %>% 
  summary()
```

```{r}
glmer(response_yn ~ scale(por_score) + (1 | country), 
      family = "binomial", d1_tml1 %>% filter(question == "godviavisions")) %>% 
  summary()
```

```{r}
glmer(response_yn ~ scale(abs_score) + (1 | country), 
      family = "binomial", d1_tml1 %>% filter(question == "godviavisions")) %>% 
  summary()
```

## Focus on other presence questions

```{r}
d1_tml2 <- d1 %>% select(country, subject_id, abs_score, por_score) %>%
  full_join(d1_byquestion %>% 
              select(country, subject_id, neartangiblegod, presencenotgod, 
                     presencedemon, beingentbody, seehearnotgod, 
                     spiritbeingencounter) %>%
              gather(question, response, -c(country, subject_id)) %>%
              mutate(response_yn = case_when(response < 1 ~ 0,
                                             response == 1 ~ 1,
                                             TRUE ~ NA_real_)))
```

```{r}
glmer(response_yn ~ scale(por_score) + (1 | question) + (1 | country), 
      family = "binomial", d1_tml2) %>% summary()
```

```{r}
glmer(response_yn ~ scale(abs_score) + (1 | question) + (1 | country), 
      family = "binomial", d1_tml2) %>% summary()
```


# Cultural invitation vs. individual difference

## Amount of variability each predictor, within each site

```{r}
d1_variance <- d1 %>% 
  select(country, site, religion, subject_id, abs_score, por_score) %>%
  gather(var, score, ends_with("_score")) %>%
  filter(!is.na(score)) %>%
  mutate(score_rescaled = case_when(var == "abs_score" ~ score/1,
                                    var == "por_score" ~ score/3)) # called pv_score in study 4
```

```{r}
bartlett.test(score_rescaled ~ var, 
              data = d1_variance %>% filter(country == "US"))

d1_variance %>% 
  filter(country == "US") %>%
  group_by(var) %>%
  summarise(variance = var(score_rescaled))
```

```{r}
bartlett.test(score_rescaled ~ var, 
              data = d1_variance %>% filter(country == "Ghana"))

d1_variance %>% 
  filter(country == "Ghana") %>%
  group_by(var) %>%
  summarise(variance = var(score_rescaled))
```

```{r}
bartlett.test(score_rescaled ~ var, 
              data = d1_variance %>% filter(country == "Thailand"))

d1_variance %>% 
  filter(country == "Thailand") %>%
  group_by(var) %>%
  summarise(variance = var(score_rescaled))
```

```{r}
bartlett.test(score_rescaled ~ var, 
              data = d1_variance %>% filter(country == "China"))

d1_variance %>% 
  filter(country == "China") %>%
  group_by(var) %>%
  summarise(variance = var(score_rescaled))
```

```{r}
bartlett.test(score_rescaled ~ var, 
              data = d1_variance %>% filter(country == "Vanuatu"))

d1_variance %>% 
  filter(country == "Vanuatu") %>%
  group_by(var) %>%
  summarise(variance = var(score_rescaled))
```

```{r}
d1_variance %>% 
  group_by(var, country) %>%
  summarise(variance = var(score_rescaled)) %>%
  ungroup() %>%
  spread(var, variance) %>%
  rename(Country = country, Absorption = abs_score, 
         `Porosity Vignettes` = por_score) %>%
  kable(digits = 2) %>%
  kable_styling()
```

```{r, fig.width = 3, fig.asp = 0.6}
d1_variance %>%
  group_by(var, country) %>%
  mutate(score_cent = scale(score_rescaled, scale = F)) %>%
  ungroup() %>%
  mutate(var = recode_factor(var,
                             "por_score" = "Porosity Vignettes",
                             "abs_score" = "Absorption")) %>%
  ggplot(aes(x = score_cent, fill = var, color = var, lty = var)) +
  facet_wrap(country ~ ., ncol = 3) +
  geom_density(alpha = 0.1) +
  scale_linetype_manual(values = c(1, 2)) +
  scale_color_brewer(palette = "Set1", direction = -1) +
  scale_fill_brewer(palette = "Set1", direction = -1) +
  labs(x = "Score (rescaled to run from 0-1, centered at the mean by country)",
       color = "Scale", fill = "Scale", lty = "Scale") +
  theme(legend.position = "bottom")
```

```{r, fig.width = 3, fig.asp = 0.8}
d1_variance %>%
  group_by(var, country, site, religion) %>%
  mutate(score_cent = scale(score_rescaled, scale = F)) %>%
  ungroup() %>%
  mutate(var = recode_factor(var,
                             "por_score" = "Porosity Vignettes",
                             "abs_score" = "Absorption")) %>%
  ggplot(aes(x = score_cent, fill = var, color = var, lty = var)) +
  facet_grid(cols = vars(country), rows = vars(site, religion)) +
  geom_density(alpha = 0.1) +
  scale_linetype_manual(values = c(1, 2)) +
  scale_color_brewer(palette = "Set1", direction = -1) +
  scale_fill_brewer(palette = "Set1", direction = -1) +
  labs(x = "Score (rescaled to run from 0-1, centered at the mean by country)",
       color = "Scale", fill = "Scale", lty = "Scale") +
  theme(legend.position = "bottom")
```

## Variance accounted for by country

```{r}
r7 <- lm(por_score_std ~ country, d1)
regtab_fun(r7, country_var1 = "country_gh", country_var2 = "country_th", country_var3 = "country_ch", country_var4 = "country_vt")
rsquared(r7)
```

```{r}
r9 <- lm(abs_score_std ~ country, d1)
rsquared(r9)
```




