---
title: "Study 1: Extra (not reported)"
subtitle: "Luhrmann, Weisman, et al."
output: 
  html_notebook:
    theme: flatly
    toc: true
    toc_float: true
---

In this notebook, we conduct additional analyses for Study 1: In-depth interviews with people of faith (not reported in the main text or the Supplemental Information of the paper).

```{r}
source("../../scripts_general/dependencies.R")
source("../../scripts_general/custom_funs.R")
source("../../scripts_general/var_recode_contrast.R")
source("../scripts_s1/s1_var_groups.R")
source("../../scripts_general/data_load.R")
```


# More on recoding ("QTS2")

```{r}
d1r_byquestion <- read_csv("../data/study1r_byquestion.csv")
```

```{r}
d1r <- read_csv("../data/study1r.csv") %>%
  rename_at(vars(contains("score")), funs(gsub("score", "recoded", .))) %>%
  full_join(d1) %>%
  mutate(country = factor(country, levels = levels_country),
         site = factor(site, levels = levels_site),
         religion = factor(religion, levels = levels_religion),
         researcher = factor(researcher, levels = levels_researcher))

contrasts(d1r$country) <- contrasts_country
contrasts(d1r$site) <- contrasts_site
contrasts(d1r$religion) <- contrasts_religion
```

## Averages, by score

```{r}
d1r %>% 
  select(country, subject_id, ends_with("recoded"), ends_with("score")) %>%
  gather(scale, score, -c(country, subject_id)) %>%
  filter(grepl("spev", scale) | grepl("other", scale)) %>%
  mutate(score_type = case_when(grepl("recoded", scale) ~ "recoded",
                                grepl("score", scale) ~ "original",
                                TRUE ~ NA_character_),
         score_type = factor(score_type, levels = c("original", "recoded")),
         scale = case_when(grepl("spev", scale) ~ "spiritual experiences",
                           grepl("other", scale) ~ "other extraordinary experiences",
                           TRUE ~ NA_character_),
         scale = factor(scale, levels = c("spiritual experiences", 
                                          "other extraordinary experiences"))) %>%
  ggplot(aes(x = scale, y = score, group = score_type)) +
  # geom_point(aes(color = score_type), alpha = 0.2,
  #            position = position_jitterdodge(jitter.width = 0.1,
  #                                            dodge.width = 0.5,
  #                                            jitter.height = 0.04)) +
  geom_pointrange(data = . %>%
                    group_by(scale, score_type) %>%
                    langcog::multi_boot_standard(col = "score", na.rm = T),
                  aes(y = mean, ymin = ci_lower, ymax = ci_upper, fill = score_type),
                  position = position_dodge(width = 0.5),
                  shape = 21, fatten = 6) +
  labs(title = "Comparing recoded scores (QTS2) to original scores (QTS1)",
       x = "Scale", y = "Score (range: 0-1)",
       fill = "Score type")
```

```{r}
d1r_long <- d1r %>% 
     select(country, subject_id, ends_with("recoded"), ends_with("score")) %>%
     gather(scale, score, -c(country, subject_id)) %>%
     filter(grepl("spev", scale) | grepl("other", scale)) %>%
     mutate(score_type = case_when(grepl("recoded", scale) ~ "recoded",
                                   grepl("score", scale) ~ "original",
                                   TRUE ~ NA_character_),
            score_type = factor(score_type, levels = c("original", "recoded")),
            scale = case_when(grepl("spev", scale) ~ "spiritual experiences",
                              grepl("other", scale) ~ "other extraordinary experiences",
                              TRUE ~ NA_character_),
            scale = factor(scale, levels = c("spiritual experiences", 
                                             "other extraordinary experiences")))

contrasts(d1r_long$scale) <- contr.sum(2)
contrasts(d1r_long$score_type) <- contr.sum(2)
```

```{r}
lmer(score ~ score_type * scale + (1 | subject_id), data = d1r_long) %>%
  summary()
```

```{r}
d1r %>% 
  select(country, subject_id, ends_with("recoded"), ends_with("score")) %>%
  gather(scale, score, -c(country, subject_id)) %>%
  filter(grepl("spev", scale) | grepl("other", scale)) %>%
  mutate(score_type = case_when(grepl("recoded", scale) ~ "recoded",
                                grepl("score", scale) ~ "original",
                                TRUE ~ NA_character_),
         score_type = factor(score_type, levels = c("original", "recoded")),
         scale = case_when(grepl("spev", scale) ~ "spiritual exp.",
                           grepl("other", scale) ~ "other exp.",
                           TRUE ~ NA_character_),
         scale = factor(scale, levels = c("spiritual exp.", 
                                          "other exp."))) %>%
  ggplot(aes(x = scale, y = score, group = score_type)) +
  facet_grid(~ country) +
  # geom_point(aes(color = score_type), alpha = 0.2,
  #            position = position_jitterdodge(jitter.width = 0.1,
  #                                            dodge.width = 0.5,
  #                                            jitter.height = 0.04)) +
  geom_pointrange(data = . %>%
                    group_by(scale, score_type, country) %>%
                    langcog::multi_boot_standard(col = "score", na.rm = T),
                  aes(y = mean, ymin = ci_lower, ymax = ci_upper, fill = score_type),
                  position = position_dodge(width = 0.5),
                  shape = 21, fatten = 6) +
  labs(title = "Comparing recoded scores (QTS2) to original scores (QTS1)",
       x = "Scale", y = "Score (range: 0-1)",
       fill = "Score type") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))
```

```{r, fig.width = 6, fig.asp = 0.8}
d1r %>% 
  select(country, site, religion, subject_id, 
         ends_with("recoded"), ends_with("score")) %>%
  gather(scale, score, -c(country, site, religion, subject_id)) %>%
  filter(grepl("spev", scale) | grepl("other", scale)) %>%
  mutate(score_type = case_when(grepl("recoded", scale) ~ "recoded",
                                grepl("score", scale) ~ "original",
                                TRUE ~ NA_character_),
         score_type = factor(score_type, levels = c("original", "recoded")),
         scale = case_when(grepl("spev", scale) ~ "spiritual exp.",
                           grepl("other", scale) ~ "other exp.",
                           TRUE ~ NA_character_),
         scale = factor(scale, levels = c("spiritual exp.", 
                                          "other exp."))) %>%
  ggplot(aes(x = scale, y = score, group = score_type)) +
  facet_grid(rows = vars(site, religion), cols = vars(country)) +
  geom_point(aes(color = score_type), alpha = 0.2,
             position = position_jitterdodge(jitter.width = 0.1,
                                             dodge.width = 0.5,
                                             jitter.height = 0.04)) +
  geom_pointrange(data = . %>%
                    group_by(scale, score_type, country, site, religion) %>%
                    langcog::multi_boot_standard(col = "score", na.rm = T),
                  aes(y = mean, ymin = ci_lower, ymax = ci_upper, fill = score_type),
                  position = position_dodge(width = 0.5),
                  shape = 21, fatten = 6) +
  labs(title = "Comparing recoded scores (QTS2) to original scores (QTS1)",
       x = "Scale", y = "Score (range: 0-1)",
       fill = "Score type", color = "Score type") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))
```

```{r}
d1r %>% 
  select(country, subject_id, coder, ends_with("recoded")) %>%
  gather(scale, score, -c(country, subject_id, coder)) %>%
  mutate(score_type = case_when(grepl("recoded", scale) ~ "recoded",
                                grepl("score", scale) ~ "original",
                                TRUE ~ NA_character_),
         score_type = factor(score_type, levels = c("original", "recoded")),
         scale = case_when(grepl("spev", scale) ~ "spiritual exp.",
                           grepl("other", scale) ~ "other exp.",
                           TRUE ~ NA_character_),
         scale = factor(scale, levels = c("spiritual exp.", 
                                          "other exp."))) %>%
  filter(grepl("spev", scale) | grepl("other", scale)) %>%
  ggplot(aes(x = scale, y = score, group = coder)) +
  facet_grid(~ country) +
  geom_point(aes(color = coder), alpha = 0.2,
             position = position_jitterdodge(jitter.width = 0.1,
                                             dodge.width = 0.5,
                                             jitter.height = 0.04)) +
  geom_pointrange(data = . %>%
                    group_by(scale, coder, country) %>%
                    langcog::multi_boot_standard(col = "score", na.rm = T),
                  aes(y = mean, ymin = ci_lower, ymax = ci_upper, fill = coder),
                  shape = 21, fatten = 5,
                  position = position_dodge(width = 0.5)) +
  labs(title = "Comparing coders in recoded dataset (QTS2)",
       x = "Scale", y = "Score (range: 0-1)", fill = "Coder", color = "Coder") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))
```

```{r}
lmer(score ~ scale * coder + (1 | subject_id), 
   data = d1r %>% 
     select(country, coder, subject_id, ends_with("recoded")) %>%
     distinct() %>%
     gather(scale, score, -c(country, subject_id, coder)) %>%
     filter(grepl("spev", scale) | grepl("other", scale)) %>%
     mutate(scale = case_when(grepl("spev", scale) ~ "spiritual experiences",
                              grepl("other", scale) ~ "other extraordinary experiences",
                              TRUE ~ NA_character_),
            scale = factor(scale, levels = c("spiritual experiences", 
                                             "other extraordinary experiences")),
            coder = factor(coder, levels = c("Nikki", "Maria", "Lucy"))),
   contrasts = list(scale = "contr.sum", 
                    coder = cbind("_NvGM" = c(1, 0, -1),
                                  "_MvGM" = c(0, 1, -1)))) %>%
  summary()
```

```{r, fig.width = 6, fig.asp = 0.8}
d1r %>% 
  select(country, site, religion, subject_id, coder, ends_with("recoded")) %>%
  gather(scale, score, -c(country, site, religion, subject_id, coder)) %>%
  mutate(score_type = case_when(grepl("recoded", scale) ~ "recoded",
                                grepl("score", scale) ~ "original",
                                TRUE ~ NA_character_),
         score_type = factor(score_type, levels = c("original", "recoded")),
         scale = case_when(grepl("spev", scale) ~ "spiritual exp.",
                           grepl("other", scale) ~ "other exp.",
                           TRUE ~ NA_character_),
         scale = factor(scale, levels = c("spiritual exp.", 
                                          "other exp."))) %>%
  filter(grepl("spev", scale) | grepl("other", scale)) %>%
  ggplot(aes(x = scale, y = score, group = coder)) +
  facet_grid(rows = vars(site, religion), cols = vars(country)) +
  geom_point(aes(color = coder), alpha = 0.2,
             position = position_jitterdodge(jitter.width = 0.1,
                                             dodge.width = 0.5,
                                             jitter.height = 0.04)) +
  geom_pointrange(data = . %>%
                    group_by(scale, coder, country, site, religion) %>%
                    langcog::multi_boot_standard(col = "score", na.rm = T),
                  aes(y = mean, ymin = ci_lower, ymax = ci_upper, fill = coder),
                  shape = 21, fatten = 5,
                  position = position_dodge(width = 0.5)) +
  geom_text(data = . %>% count(country, site, religion, coder, scale),
             aes(y = 0, label = paste0("n=", n), color = coder), 
            position = position_dodge(width = 1)) +
  labs(title = "Comparing coders in recoded dataset (QTS2)",
       x = "Scale", y = "Score (range: 0-1)", fill = "Coder", color = "Coder") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))
```



## Averages, by question

```{r, fig.width = 6, fig.asp = 0.4}
d1r_byquestion %>% 
  select(country, site, religion, subject_id, 
         !!s1_var_spev, !!s1_var_other) %>%
  gather(question, recoded, -c(country, site, religion, subject_id)) %>%
  full_join(d1_byquestion %>%
              select(country, site, religion, subject_id, 
                     !!s1_var_spev, !!s1_var_other) %>%
              gather(question, original, -c(country, site, religion, subject_id))) %>%
  gather(response_type, response, c(original, recoded)) %>%
  mutate(question = factor(question, levels = c(s1_var_spev, s1_var_other)),
         response_type = factor(response_type, levels = c("original", "recoded"))) %>%
  ggplot(aes(x = question, y = response, group = response_type)) +
  geom_pointrange(data = . %>%
                    group_by(question, response_type) %>%
                    langcog::multi_boot_standard(col = "response", na.rm = T),
                  aes(y = mean, ymin = ci_lower, ymax = ci_upper,
                      fill = response_type),
                  position = position_dodge(width = 0.5),
                  shape = 21, fatten = 6) +
  labs(title = "Comparing recoded scores (QTS2) to original scores (QTS1)",
       x = "Question", y = "Response (range: 0-1)",
       fill = "Response type") +
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))
```

```{r}
d1r_byquestion %>% 
  select(country, site, religion, subject_id, 
         !!s1_var_spev, !!s1_var_other) %>%
  gather(question, recoded, -c(country, site, religion, subject_id)) %>%
  full_join(d1_byquestion %>%
              select(country, site, religion, subject_id, 
                     !!s1_var_spev, !!s1_var_other) %>%
              gather(question, original, -c(country, site, religion, subject_id))) %>%
  gather(response_type, response, c(original, recoded)) %>%
  mutate(question = factor(question, levels = c(s1_var_spev, s1_var_other)),
         response_type = factor(response_type, levels = c("original", "recoded"))) %>%
  filter(question == "seehearnotgod") %>%
  count(response_type, response) %>%
  spread(response, n)
```

```{r}
d1r_byquestion %>% 
  select(country, site, religion, subject_id, 
         !!s1_var_spev, !!s1_var_other) %>%
  gather(question, recoded, -c(country, site, religion, subject_id)) %>%
  full_join(d1_byquestion %>%
              select(country, site, religion, subject_id, 
                     !!s1_var_spev, !!s1_var_other) %>%
              gather(question, original, -c(country, site, religion, subject_id))) %>%
  mutate(question = factor(question, levels = c(s1_var_spev, s1_var_other))) %>%
  filter(question == "seehearnotgod") %>%
  mutate(match = (original == recoded)) %>%
  count(match) %>%
  mutate(prop = n/sum(n))
```


# Cultural invitation vs. individual difference

## Amount of variability each predictor, within each site

```{r}
d1_variance <- d1 %>% 
  select(country, site, religion, subject_id, abs_score, pv_score) %>%
  gather(var, score, ends_with("_score")) %>%
  filter(!is.na(score)) %>%
  mutate(score_rescaled = case_when(var == "abs_score" ~ score/1,
                                    var == "pv_score" ~ score/3)) # called pv_score in study 4
```

```{r}
bartlett.test(score_rescaled ~ var, 
              data = d1_variance %>% filter(country == "US"))

d1_variance %>% 
  filter(country == "US") %>%
  group_by(var) %>%
  summarise(variance = var(score_rescaled))
```

```{r}
bartlett.test(score_rescaled ~ var, 
              data = d1_variance %>% filter(country == "Ghana"))

d1_variance %>% 
  filter(country == "Ghana") %>%
  group_by(var) %>%
  summarise(variance = var(score_rescaled))
```

```{r}
bartlett.test(score_rescaled ~ var, 
              data = d1_variance %>% filter(country == "Thailand"))

d1_variance %>% 
  filter(country == "Thailand") %>%
  group_by(var) %>%
  summarise(variance = var(score_rescaled))
```

```{r}
bartlett.test(score_rescaled ~ var, 
              data = d1_variance %>% filter(country == "China"))

d1_variance %>% 
  filter(country == "China") %>%
  group_by(var) %>%
  summarise(variance = var(score_rescaled))
```

```{r}
bartlett.test(score_rescaled ~ var, 
              data = d1_variance %>% filter(country == "Vanuatu"))

d1_variance %>% 
  filter(country == "Vanuatu") %>%
  group_by(var) %>%
  summarise(variance = var(score_rescaled))
```

```{r}
d1_variance %>% 
  group_by(var, country) %>%
  summarise(variance = var(score_rescaled)) %>%
  ungroup() %>%
  spread(var, variance) %>%
  rename(Country = country, Absorption = abs_score, 
         `Porosity Vignettes` = pv_score) %>%
  kable(digits = 2) %>%
  kable_styling()
```

```{r, fig.width = 3, fig.asp = 0.6}
d1_variance %>%
  group_by(var, country) %>%
  mutate(score_cent = scale(score_rescaled, scale = F)) %>%
  ungroup() %>%
  mutate(var = recode_factor(var,
                             "pv_score" = "Porosity Vignettes",
                             "abs_score" = "Absorption")) %>%
  ggplot(aes(x = score_cent, fill = var, color = var, lty = var)) +
  facet_wrap(country ~ ., ncol = 3) +
  geom_density(alpha = 0.1) +
  scale_linetype_manual(values = c(1, 2)) +
  scale_color_brewer(palette = "Set1", direction = -1) +
  scale_fill_brewer(palette = "Set1", direction = -1) +
  labs(x = "Score (rescaled to run from 0-1, centered at the mean by country)",
       color = "Scale", fill = "Scale", lty = "Scale") +
  theme(legend.position = "bottom")
```

```{r, fig.width = 3, fig.asp = 0.8}
d1_variance %>%
  group_by(var, country, site, religion) %>%
  mutate(score_cent = scale(score_rescaled, scale = F)) %>%
  ungroup() %>%
  mutate(var = recode_factor(var,
                             "pv_score" = "Porosity Vignettes",
                             "abs_score" = "Absorption")) %>%
  ggplot(aes(x = score_cent, fill = var, color = var, lty = var)) +
  facet_grid(cols = vars(country), rows = vars(site, religion)) +
  geom_density(alpha = 0.1) +
  scale_linetype_manual(values = c(1, 2)) +
  scale_color_brewer(palette = "Set1", direction = -1) +
  scale_fill_brewer(palette = "Set1", direction = -1) +
  labs(x = "Score (rescaled to run from 0-1, centered at the mean by country)",
       color = "Scale", fill = "Scale", lty = "Scale") +
  theme(legend.position = "bottom")
```

## Variance accounted for by country

```{r}
r7 <- lm(pv_score_std ~ country, d1)
regtab_fun(r7, country_var1 = "country_gh", country_var2 = "country_th", country_var3 = "country_ch", country_var4 = "country_vt")
rsquared(r7)
```

```{r}
r9 <- lm(abs_score_std ~ country, d1)
rsquared(r9)
```


# Country, site, and religion as fixed effects

```{r}
r10 <- lm(spev_score_std ~ pv_score_std * abs_score_std * 
            country * site * religion, d1)
# summary(r10)
```

```{r}
regtab_fun(r10) %>% regtab_style_fun(row_emph = 2:3)
```

```{r}
r11 <- lm(spev_score_std ~ pv_score_std * abs_score_std * country * religion, d1)
# summary(r11)
```

```{r}
regtab_fun(r11) %>% regtab_style_fun(row_emph = 2:3)
```

```{r}
r12 <- lm(spev_score_std ~ pv_score_std * abs_score_std * country * site, d1)
# summary(r12)
```

```{r}
regtab_fun(r12) %>% regtab_style_fun(row_emph = 2:3)
```


# Predicting Other Extraordinary Events

```{r}
r3 <- lmer(other_score_std ~ pv_score_std * abs_score_std +
             (1 | country/site/religion),
             # (1 | country/religion),
           data = d1)
summary(r3)
```

```{r}
rsquared(r3)
```

```{r}
regtab_fun(r3, por_name = "Porosity Vignettes") %>%
  regtab_style_fun(row_emph = 2:3)
```

```{r}
regtab_ran_fun(r3) %>% regtab_style_fun()
```

## Recoding

```{r}
rr3 <- lmer(other_recoded_std ~ pv_score_std * abs_score_std +
              (1 | country/site/religion),
            # (1 | country/religion),
            data = d1r)
summary(rr3)
```

```{r}
piecewiseSEM::rsquared(rr3)
```

```{r}
regtab_fun(rr3, por_name = "Porosity Vignettes") %>% 
  regtab_style_fun(row_emph = 2:3)
```

```{r}
regtab_ran_fun(rr3) %>% regtab_style_fun()
```

