---
title: "Study 1: Supplemental analyses"
subtitle: "Luhrmann, Weisman, et al."
output: 
  html_notebook:
    theme: flatly
    toc: true
    toc_float: true
---

In this notebook, we conduct additional analyses for Study 1: In-depth interviews with people of faith (as discussed in Supplemental Information).

```{r}
source("../../scripts_general/dependencies.R")
source("../../scripts_general/custom_funs.R")
source("../../scripts_general/var_recode_contrast.R")
source("../../scripts_general/data_load.R")
source("../scripts_s1/s1_var_groups.R")
```


# Missing data

```{r}
d1 %>% filter(!is.na(pv_score_std),
              !is.na(abs_score_std),
              !is.na(spev_score_std)) %>% 
  distinct(subject_id) %>%
  left_join(d1_byquestion %>%
              select(subject_id, s1_var_pv, s1_var_abs, 
                     s1_var_spev, s1_var_other) %>%
              distinct()) %>%
  gather(question, response, -subject_id) %>%
  mutate(scale = case_when(
    question %in% s1_var_pv ~ "Porosity Vignettes",
    question %in% s1_var_abs ~ "Absorption",
    question %in% s1_var_spev ~ "Spiritual Events",
    question %in% s1_var_other ~ "Other Extraordinary Events")) %>%
  count(scale, response) %>%
  group_by(scale) %>%
  mutate(prop = n/sum(n)) %>%
  ungroup() %>%
  filter(is.na(response))
```

```{r}
d1 %>% filter(!is.na(pv_score_std),
              !is.na(abs_score_std),
              !is.na(spev_score_std)) %>% 
  distinct(subject_id) %>%
  left_join(d1_byquestion %>%
              select(subject_id, s1_var_pv, s1_var_abs, 
                     s1_var_spev, s1_var_other) %>%
              distinct() %>%
              gather(question, response, -subject_id)) %>%
  mutate(scale = case_when(
    question %in% s1_var_pv ~ "Porosity Vignettes",
    question %in% s1_var_abs ~ "Absorption",
    question %in% s1_var_spev ~ "Spiritual Events",
    question %in% s1_var_other ~ "Other Extraordinary Events")) %>%
  count(scale, subject_id, response) %>%
  filter(is.na(response)) %>%
  count(scale) %>%
  mutate(prop = n/306)
```


# Reliability

## Spiritual Events

```{r}
d_alpha_spirit <- data.frame()
for(i in c(levels(d1$country), "ALL")){
  res <- data.frame(country = i, 
                    alpha = alpha_fun(d1_byquestion, 
                                      which_vars = s1_var_spev,
                                      which_country = i))
  d_alpha_spirit <- bind_rows(d_alpha_spirit, res)
  rm(res)
}
```

```{r}
d_alpha_other <- data.frame()
for(i in c(levels(d1$country), "ALL")){
  res <- data.frame(country = i, 
                    alpha = alpha_fun(d1_byquestion, 
                                      which_vars = s1_var_other,
                                      which_country = i))
  d_alpha_other <- bind_rows(d_alpha_other, res)
  rm(res)
}
```

```{r}
d_alpha_por <- data.frame()
for(i in c(levels(d1$country), "ALL")){
  res <- data.frame(country = i, 
                    alpha = alpha_fun(d1_byquestion, 
                                      which_vars = s1_var_pv,
                                      which_country = i))
  d_alpha_por <- bind_rows(d_alpha_por, res)
  rm(res)
}
```

```{r}
d_alpha_abs <- data.frame()
for(i in c(levels(d1$country), "ALL")){
  res <- data.frame(country = i, 
                    alpha = alpha_fun(d1_byquestion, 
                                      which_vars = s1_var_abs,
                                      which_country = i))
  d_alpha_abs <- bind_rows(d_alpha_abs, res)
  rm(res)
}
```

```{r}
bind_rows(d_alpha_por %>% mutate(scale = "Porosity Vignettes"),
          d_alpha_abs %>% mutate(scale = "Absorption"),
          d_alpha_spirit %>% mutate(scale = "Spiritual Events"),
          d_alpha_other %>% mutate(scale = "Other Extraordinary Events")) %>%
  select(scale, country, alpha) %>%
  mutate(scale = factor(scale,
                        levels = c("Porosity Vignettes", "Absorption", 
                                   "Spiritual Events",
                                   "Other Extraordinary Events")), 
         country = factor(country, levels = c(levels_country, "ALL"))) %>%
  spread(country, alpha) %>%
  kable(digits = 2) %>%
  kable_styling() %>%
  column_spec(7, bold = T)
```


# Robustness check

```{r, include = F}
df_all <- data.frame()
for(i in s1_var_spev){
  df_temp <- score_fun(df = d1_byquestion %>% 
                         select(country, subject_id, s1_var_spev), 
                       var_omit = i) %>%
    mutate(omitted = i)
  df_all <- bind_rows(df_temp, df_all)
}
```

```{r, fig.width = 10, fig.asp = 0.2, include = F}
df_all %>%
  ggplot(aes(x = omitted, y = score, color = country)) +
  facet_grid(~country) +
  geom_jitter(width = 0.3, height = 0, alpha = 0.5, show.legend = F) +
  geom_pointrange(data = . %>% group_by(country, omitted) %>%
                    langcog::multi_boot_standard(col = "score", na.rm = T),
                  aes(y = mean, ymin = ci_lower, ymax = ci_upper),
                  color = "black") +
  scale_color_brewer(palette = "Dark2") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))
```

```{r, fig.width = 5, fig.asp = 1.2, include = F}
df_all %>%
  ggplot(aes(x = country, y = score, color = country)) +
  facet_wrap(~omitted) +
  geom_jitter(width = 0.3, height = 0, alpha = 0.5, show.legend = F) +
  geom_pointrange(data = . %>% group_by(country, omitted) %>%
                    langcog::multi_boot_standard(col = "score", na.rm = T),
                  aes(y = mean, ymin = ci_lower, ymax = ci_upper),
                  color = "black") +
  scale_color_brewer(palette = "Dark2") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))
```

```{r}
reg_check_fun <- function(df, var_omit){
  d <- score_fun(df = df, var_omit = var_omit) %>% 
    mutate(score_std = scale(score)) %>% full_join(d1)
  
  # run primary analysis
  r0 <- lmer(score_std ~ pv_score_std * abs_score_std +
               (1 | country/site/religion), data = d)
  r0_tab <- summary((r0))$coefficients[] %>%
    data.frame() %>%
    rownames_to_column("param") %>%
    rename(b = Estimate, se = Std..Error, t = t.value, p = Pr...t..) %>%
    mutate(omitted = var_omit,
           signif = case_when(p < 0.001 ~ "***",
                              p < 0.01 ~ "**",
                              p < 0.05 ~ "*",
                              p < 0.1 ~ "+",
                              TRUE ~ "")) %>%
    select(omitted, param, b, se, df, t, p, signif) %>%
    filter(param != "(Intercept)")
  
  reg_tab <- r0_tab
  return(reg_tab)
}
```

```{r}
reg_check_df <- data.frame()
for(i in s1_var_spev){
  temp_df <- reg_check_fun(df = d1_byquestion %>% 
                             select(country, subject_id, s1_var_spev), 
                           var_omit = i)
  reg_check_df <- bind_rows(reg_check_df, temp_df)
}
```

```{r, fig.width = 4, fig.asp = 0.7}
reg_check_df %>%
  full_join(reg_check_fun(df = d1_byquestion %>% 
                            select(country, subject_id, s1_var_spev), 
                          var_omit = NA_character_) %>%
              mutate(omitted = "ALL VARIABLES INCLUDED")) %>%
  mutate(mod_type = case_when(omitted == "ALL VARIABLES INCLUDED" ~ "all",
                              TRUE ~ "test"),
         signif_cat = ifelse(signif == "", F, T),
         omitted = factor(omitted, 
                          levels = c("ALL VARIABLES INCLUDED", s1_var_spev)),
         param = recode_factor(param,
                               "pv_score_std" = "Porosity Vignettes",
                               "abs_score_std" = "Absorption",
                               "pv_score_std:abs_score_std" = "Interaction")) %>%
  ggplot(aes(x = b, y = reorder(omitted, desc(omitted)), 
             shape = mod_type, size = mod_type, fill = signif)) + 
  facet_grid(~ param) +
  geom_vline(xintercept = 0, lty = 2) +
  geom_point(show.legend = F) +
  scale_shape_manual(values = c(23, 21)) +
  scale_fill_manual(values = c("black", "dodgerblue")) +
  scale_size_manual(values = c(3, 1.5)) +
  labs(title = "Omitting 1 variable at a time from Spiritual Events scale",
       subtitle = "Primary analysis (mixed effects linear regression); blue = significant (p<0.05)",
       x = "β", y = "Question omitted from Spiritual Events score") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))
```

```{r}
reg_brms_check_fun <- function(df, var_omit){
  d <- score_fun(df = df, var_omit = var_omit) %>%
    mutate(score_std = scale(score)) %>% full_join(d1)
  
  r0 <- brm(score_std ~ pv_score_std * abs_score_std + 
              (1 | country/site/religion), data = d,
            control = list(adapt_delta = 0.99),
            seed = 1234, cores = 4, chains = 4)
  
  r0_tab <- fixef(r0) %>%
    data.frame() %>%
    rownames_to_column("param") %>%
    rename(b = Estimate, se = Est.Error, ci_lower = Q2.5, ci_upper = Q97.5) %>%
    mutate(omitted = var_omit,
           nonzero = case_when(ci_lower * ci_upper > 0 ~ "*",
                               TRUE ~ "")) %>%
    select(omitted, param, b, se, ci_lower, ci_upper, nonzero)
  
  reg_tab <- r0_tab
  return(reg_tab)
}
```

XX BOOKMARK

```{r}
# reg_brms_check_df <- data.frame()
# for(i in s1_var_spev){
#   temp_df <- reg_brms_check_fun(df = d1_byquestion %>%
#                                   select(country, subject_id, s1_var_spev),
#                                 var_omit = i)
#   reg_brms_check_df <- bind_rows(reg_brms_check_df, temp_df)
#   saveRDS(reg_brms_check_df, "./models/reg_brms_check_df.RDS")
#   rm(temp_df)
# }

reg_brms_check_df <- readRDS("./models/reg_brms_check_df.RDS")
```

```{r}
# reg_brms_check_all <- reg_brms_check_fun(
#   df = d1_byquestion %>% select(country, subject_id, s1_var_spev),
#   var_omit = NA_character_)
# 
# saveRDS(reg_brms_check_all, "./models/reg_brms_check_all.RDS")

reg_brms_check_all <- readRDS("./models/reg_brms_check_all.RDS")
```

```{r, fig.width = 4, fig.asp = 0.7}
reg_brms_check_df %>%
  full_join(reg_brms_check_all %>%
              mutate(omitted = "ALL VARIABLES INCLUDED")) %>%
  filter(param != "Intercept") %>%
  mutate(param = recode_factor(param,
                               "pv_score_std" = "Porosity",
                               "abs_score_std" = "Absorption",
                               "pv_score_std:abs_score_std" = "Interaction"),
         omitted = factor(omitted, 
                          levels = c("ALL VARIABLES INCLUDED", s1_var_spev))) %>%
  mutate(mod_type = case_when(omitted == "ALL VARIABLES INCLUDED" ~ "all",
                              TRUE ~ "test")) %>%
  ggplot(aes(x = b, y = reorder(omitted, desc(omitted)),
             shape = mod_type, fill = nonzero)) + 
  facet_grid(~ param) +
  geom_vline(xintercept = 0, lty = 2) +
  geom_errorbarh(aes(xmin = ci_lower, xmax = ci_upper), height = 0) +
  geom_point(aes(size = mod_type), show.legend = F) +
  scale_shape_manual(values = c(23, 21)) +
  scale_size_manual(values = c(3, 1.5)) +
  scale_fill_manual(values = c("black", "dodgerblue")) +
  labs(title = "Omitting 1 variable at a time from Spiritual Events scale",
       subtitle = "Bayesian version of primary analysis; blue = non-zero",
       x = "β", y = "Question omitted from Spiritual Events score")
```


# Recoded dataset

```{r}
d1r_byquestion <- read_csv("../data/study1r_byquestion.csv")
```

```{r}
d1r <- read_csv("../data/study1r.csv") %>%
  rename_at(vars(contains("score")), funs(gsub("score", "recoded", .))) %>%
  full_join(d1) %>%
  mutate(country = factor(country, levels = levels_country),
         site = factor(site, levels = levels_site),
         religion = factor(religion, levels = levels_religion),
         researcher = factor(researcher, levels = levels_researcher))

contrasts(d1r$country) <- contrasts_country
contrasts(d1r$site) <- contrasts_site
contrasts(d1r$religion) <- contrasts_religion
```


## Comparison to original dataset

```{r}
# omit subjects with no data from interviewers (all NAs)
s1_subj_int_nodata <- d1_byquestion %>% 
  select(subject_id, s1_var_spev, s1_var_other) %>%
  gather(question, response, -subject_id) %>%
  count(subject_id, response) %>%
  filter(is.na(response), n == 29) %>%
  select(subject_id)

# omit subjects with no data from coders (all NAs)
s1_subj_cod_nodata <- d1r_byquestion %>% 
  select(subject_id, s1_var_spev, s1_var_other) %>%
  gather(question, response, -subject_id) %>%
  count(subject_id, response) %>%
  filter(is.na(response), n == 29) %>%
  select(subject_id)
```

```{r}
d1r_irr <- full_join(
  d1_byquestion %>% 
    filter(!subject_id %in% c(s1_subj_int_nodata$subject_id, 
                              s1_subj_cod_nodata$subject_id)) %>%
    select(country, site, religion, subject_id, s1_var_spev, s1_var_other) %>%
    gather(question, response, -c(country, site, religion, subject_id)),
  d1r_byquestion %>% 
    filter(!subject_id %in% c(s1_subj_int_nodata$subject_id, 
                              s1_subj_cod_nodata$subject_id)) %>%
    select(country, site, religion, subject_id, s1_var_spev, s1_var_other) %>%
    gather(question, recoded, -c(country, site, religion, subject_id))) %>%
  mutate(agree = case_when(is.na(recoded) & is.na(response) ~ NA_real_,
                           is.na(recoded) | is.na(response) ~ 0,
                           # is.na(recoded) | is.na(response) ~ NA_real_,
                           recoded == response ~ 1,
                           recoded != response ~ 0,
                           TRUE ~ NA_real_),
         question = factor(question, levels = c(s1_var_spev, s1_var_other)),
         scale = case_when(question %in% s1_var_spev ~ "spiritual experiences",
                           question %in% s1_var_other ~ "other experiences",
                           TRUE ~ NA_character_),
         scale = factor(scale, 
                        levels = c("spiritual experiences", "other experiences")),
         country = factor(country, levels = levels_country),
         site = factor(site, levels = levels_site),
         religion = factor(religion, levels = levels_religion))

contrasts(d1r_irr$country) <- contrasts_country
contrasts(d1r_irr$site) <- contrasts_site
contrasts(d1r_irr$religion) <- contrasts_religion
```

```{r}
s1r_perag_df <- d1r_irr %>%
  group_by(scale, question) %>%
  summarise(percent_agree = mean(agree, na.rm = T)) %>%
  ungroup() %>%
  mutate(reliability = case_when(percent_agree < 0.7 ~ "<70%",
                                 percent_agree < 0.8 ~ "70-80%",
                                 percent_agree < 0.9 ~ "80-90%",
                                 percent_agree <= 1 ~ "90-100%",
                                 TRUE ~ NA_character_),
         reliability = factor(reliability, 
                              levels = c("<70%", "70-80%", 
                                         "80-90%", "90-100%")))
```

```{r}
s1r_perag_df %>% filter(scale == "spiritual experiences") %>% arrange(percent_agree)
s1r_perag_df %>% filter(scale == "spiritual experiences") %>% count(reliability) %>% mutate(prop = n/sum(n))
s1r_perag_df %>% 
  mutate(scale = recode_factor(scale,
                               "spiritual experiences" = "spiritual",
                               "other experiences" = "other")) %>%
  ggplot(aes(x = question, y = percent_agree, color = reliability)) + 
  facet_grid(~ scale, scales = "free", space = "free") +
  geom_point() +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
  scale_color_brewer(palette = "RdYlGn", direction = 1, drop = F) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1,
                                   color = ifelse(s1r_perag_df$reliability == "<70%",
                                                  "#d7191c", "black"))) +
  labs(title = "Comparing QTS1 vs. QTS2",
       x = "Question", y = "Percent agreement")
```

```{r}
s1r_icc_df <- data.frame(question = character(), icc = numeric())
for(i in c(s1_var_spev, s1_var_other)){
  temp_icc <- icc_fun(d1r_irr, var_name = i, which_model = "oneway")
  temp_res <- data.frame(question = i, icc = temp_icc)
  s1r_icc_df <- full_join(s1r_icc_df, temp_res)
  rm(temp_res, i)
}

s1r_icc_df <- s1r_icc_df %>%
  mutate(question = factor(question, levels = c(s1_var_spev, s1_var_other)),
         reliability = case_when(icc < 0.5 ~ "poor",
                                 icc < 0.75 ~ "moderate",
                                 icc < 0.9 ~ "good", 
                                 icc <= 1 ~ "excellent",
                                 TRUE ~ NA_character_),
         reliability = factor(reliability, 
                              levels = c("poor", "moderate", 
                                         "good", "excellent")),
         scale = case_when(question %in% s1_var_spev ~ "spiritual experiences",
                           question %in% s1_var_other ~ "other experiences",
                           TRUE ~ NA_character_),
         scale = factor(scale, 
                        levels = c("spiritual experiences", "other experiences")))
```

```{r}
# s1r_icc_df %>% arrange(icc)
s1r_icc_df %>% count(reliability) %>% mutate(prop = n/sum(n))

s1r_icc_df %>% 
  mutate(scale = recode_factor(scale,
                               "spiritual experiences" = "spiritual",
                               "other experiences" = "other")) %>%
  ggplot(aes(x = question, y = icc, color = reliability)) + 
  facet_grid(~ scale, scales = "free", space = "free") +
  geom_point() +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
  scale_color_brewer(palette = "RdYlGn", direction = 1, drop = F) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1,
                                   color = ifelse(s1r_icc_df$reliability == "poor",
                                                  "#d7191c", "black"))) +
  labs(title = "Comparing QTS1 vs. QTS2",
       x = "Question", y = "Intraclass correlation coefficient (ICC)")
```

```{r}
s1r_perag_df %>% 
  select(question, percent_agree) %>%
  mutate(percent_agree = paste0(round(percent_agree * 100), "%")) %>%
  full_join(s1r_icc_df %>% select(question, icc)) %>%
  arrange(question) %>% 
  kable(digits = 2) %>% 
  kable_styling()
```

```{r}
s1_icc_poor <- s1r_icc_df$question[s1r_icc_df$reliability == "poor"] %>% 
  as.character()
```

```{r}
# make dataset omitting 4 items with "poor" ICC from spiritual experiences
d1r_mod <- score_fun(d1r_byquestion %>% 
                       select(country, subject_id, !!s1_var_spev),
                     var_omit = s1_icc_poor) %>%
  rename(spirit_mod_recoded = score) %>%
  full_join(score_fun(d1_byquestion %>%
                        select(country, subject_id, !!s1_var_spev),
                      var_omit = s1_icc_poor) %>%
              rename(spirit_mod_score = score)) %>%
  mutate(spirit_mod_recoded_std = scale(spirit_mod_recoded),
         spirit_mod_score_std = scale(spirit_mod_score)) %>%
  group_by(country) %>%
  mutate(spirit_mod_recoded_std2 = scale(spirit_mod_recoded),
         spirit_mod_score_std2 = scale(spirit_mod_score)) %>%
  ungroup() %>%
  full_join(d1r) %>%
  mutate(country = factor(country, levels = levels_country))

contrasts(d1r_mod$country) <- contrasts_country
```

## Primary analysis

### Recoded (full scale)

```{r}
rr1 <- lmer(spev_recoded_std ~ pv_score_std * abs_score_std +
              (1 | country/site/religion),
            data = d1r)
summary(rr1)
```

```{r}
piecewiseSEM::rsquared(rr1)
```

```{r}
regtab_fun(rr1, por_var = "pv_score_std", por_name = "Porosity Vignettes") %>% 
  regtab_style_fun(row_emph = 2:3)
```

```{r}
regtab_ran_fun(rr1) %>% regtab_style_fun()
```

### Original (limited scale)

```{r}
rr1a <- lmer(spirit_mod_score_std ~ pv_score_std * abs_score_std +
               (1 | country/site/religion),
             data = d1r_mod,
             control = lmerControl(optimizer = "bobyqa",
                                 optCtrl = list(maxfun = 2e5)))
summary(rr1a)
```

```{r}
piecewiseSEM::rsquared(rr1a)
```

```{r}
regtab_fun(rr1a, por_var = "pv_score_std", por_name = "Porosity Vignettes") %>% 
  regtab_style_fun(row_emph = 2:3)
```

```{r}
regtab_ran_fun(rr1a) %>% regtab_style_fun()
```

### Recoded (limited scale)

```{r}
rr1b <- lmer(spirit_mod_recoded_std ~ pv_score_std * abs_score_std +
               # (1 | country/site/religion), # fails to converge
               (1 | country/religion),
             data = d1r_mod)
summary(rr1b)
```

```{r}
piecewiseSEM::rsquared(rr1b)
```

```{r}
regtab_fun(rr1b, por_var = "pv_score_std", por_name = "Porosity Vignettes") %>% 
  regtab_style_fun(row_emph = 2:3)
```

```{r}
regtab_ran_fun(rr1b) %>% regtab_style_fun()
```

### Comparison of models

```{r}
r1 <- lmer(spev_score_std ~ pv_score_std * abs_score_std +
             (1 | country/site/religion),
           data = d1,
           control = lmerControl(optimizer = "bobyqa",
                                 optCtrl = list(maxfun = 2e5)))

r1_bayes <- readRDS("./models/r1_bayes.RDS")
```

```{r}
r1_comp_df <- bind_rows(
  summary(r1)$coefficients %>% 
    data.frame() %>%
    rownames_to_column("Parameter") %>%
    mutate(Dataset = "Original, all items"),
  summary(rr1)$coefficients %>% 
    data.frame() %>%
    rownames_to_column("Parameter") %>%
    mutate(Dataset = "Recoded, all items"),
  summary(rr1a)$coefficients %>% 
    data.frame() %>%
    rownames_to_column("Parameter") %>%
    mutate(Dataset = "Original, dropping 4 items"),
  summary(rr1b)$coefficients %>% 
    data.frame() %>%
    rownames_to_column("Parameter") %>%
    mutate(Dataset = "Recoded, dropping 4 items")) %>%
  mutate_at(vars(Estimate, Std..Error, df, t.value, Pr...t..), 
            funs(as.numeric)) %>%
  mutate(Parameter = recode_factor(Parameter,
                                   "(Intercept)" = "Intercept",
                                   "pv_score_std" = "Porosity Vignettes", 
                                   "abs_score_std" = "Absorption",
                                   "pv_score_std:abs_score_std" = "Porosity Vignettes × Absorption"))
```

```{r}
r1_comp_df %>%
  filter(Dataset == "Original, all items") %>%
  select(Parameter, Estimate) %>%
  rename(`Original β` = Estimate) %>%
  full_join(r1_comp_df %>%
              filter(Dataset != "Original, all items") %>%
              select(Dataset, Parameter, Estimate) %>%
              rename(`New β` = Estimate)) %>%
  mutate(`New β - Original β` = `New β` - `Original β`) %>%
  kable(digits = 2) %>%
  kable_styling() %>%
  collapse_rows(1:2)
```

```{r}
r1_comp_df %>% 
  filter(Parameter != "Intercept") %>%
  ggplot(aes(x = Dataset, y = Estimate)) +
  facet_grid(~ Parameter) +
  geom_hline(yintercept = 0, lty = 2) +
  geom_point() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
  labs(title = "Comparing primary analysis across different datasets (Study 1)",
       subtitle = "Mixed effects linear regression:\nlmer(spiritual experience ~ absorption * porosity + (1 | country/site/religion)",
       y = "β")
```


## Attempting to fit more complex random effects structures

```{r}
# more complex random effects structures: NOT REPORTED
rr1w <- lmer(spev_recoded_std ~ pv_score_std * abs_score_std +
               (1 + pv_score_std * abs_score_std | country/site/religion), 
             data = d1r) # singular
rr1x <- lmer(spev_recoded_std ~ pv_score_std * abs_score_std +
               (1 + pv_score_std * abs_score_std || country/site/religion), 
             data = d1r) # singular, failed to converge
rr1y <- lmer(spev_recoded_std ~ pv_score_std * abs_score_std +
               (1 + pv_score_std + abs_score_std | country/site/religion), 
             data = d1r) # singular
rr1z <- lmer(spev_recoded_std ~ pv_score_std * abs_score_std +
               (1 + pv_score_std + abs_score_std || country/site/religion), 
             data = d1r) # singular
```

## Bayesian regression

### Recoded (full scale)

```{r}
# rr1_bayes <- brm(spev_recoded_std ~ pv_score_std * abs_score_std +
#                   (1 | country/site/religion), d1r,
#                 control = list(adapt_delta = 0.999),
#                 seed = 1234, cores = 4, chains = 4)
# saveRDS(rr1_bayes, "./models/rr1_bayes.RDS")

rr1_bayes <- readRDS("./models/rr1_bayes.RDS")

summary(rr1_bayes)
```

```{r}
bayes_R2(rr1_bayes)
```

```{r}
regtab_fun(rr1_bayes, por_var = "pv_score_std", por_name = "Porosity Vignettes") %>% 
  regtab_style_fun(row_emph = 2:3)
```

```{r}
regtab_ran_fun(rr1_bayes) %>% regtab_style_fun()
```

### Original (limited scale)

```{r}
# rr1a_bayes <- brm(spirit_mod_score_std ~ pv_score_std * abs_score_std +
#                   (1 | country/site/religion), d1r_mod,
#                 control = list(adapt_delta = 0.999),
#                 seed = 1234, cores = 4, chains = 4)
# saveRDS(rr1a_bayes, "./models/rr1a_bayes.RDS")

rr1a_bayes <- readRDS("./models/rr1a_bayes.RDS")

summary(rr1a_bayes)
```

```{r}
bayes_R2(rr1a_bayes)
```

```{r}
regtab_fun(rr1a_bayes, por_var = "pv_score_std", por_name = "Porosity Vignettes") %>% 
  regtab_style_fun(row_emph = 2:3)
```

```{r}
regtab_ran_fun(rr1a_bayes) %>% regtab_style_fun()
```

### Recoded (limited scale)

```{r}
# rr1b_bayes <- brm(spirit_mod_recoded_std ~ pv_score_std * abs_score_std +
#                   (1 | country/site/religion), d1r_mod,
#                 control = list(adapt_delta = 0.999),
#                 seed = 1234, cores = 4, chains = 4)
# saveRDS(rr1b_bayes, "./models/rr1b_bayes.RDS")

rr1b_bayes <- readRDS("./models/rr1b_bayes.RDS")

summary(rr1b_bayes)
```

```{r}
bayes_R2(rr1b_bayes)
```

```{r}
regtab_fun(rr1b_bayes, por_var = "pv_score_std", por_name = "Porosity Vignettes") %>% 
  regtab_style_fun(row_emph = 2:3)
```

```{r}
regtab_ran_fun(rr1b_bayes) %>% regtab_style_fun()
```

## Comparison of models

```{r}
r1_bayes_comp_df <- bind_rows(
  fixef(r1_bayes) %>% data.frame() %>% 
    rownames_to_column("Parameter") %>%
    mutate(Dataset = "Original, all items"),
  fixef(rr1_bayes) %>% data.frame() %>% 
    rownames_to_column("Parameter") %>%
    mutate(Dataset = "Recoded, all items"),
  fixef(rr1a_bayes) %>% data.frame() %>% 
    rownames_to_column("Parameter") %>%
    mutate(Dataset = "Original, dropping 4 items"),
  fixef(rr1b_bayes) %>% data.frame() %>% 
    rownames_to_column("Parameter") %>%
    mutate(Dataset = "Recoded, dropping 4 items")) %>%
  mutate_at(vars(Estimate, Est.Error, Q2.5, Q97.5), funs(as.numeric)) %>%
  mutate(Parameter = recode_factor(Parameter,
                                   "Intercept" = "Intercept",
                                   "pv_score_std" = "Porosity Vignettes", 
                                   "abs_score_std" = "Absorption",
                                   "pv_score_std:abs_score_std" = "Porosity Vignettes × Absorption"))
```

```{r}
r1_bayes_comp_df %>%
  filter(Dataset == "Original, all items") %>%
  select(Parameter, Estimate) %>%
  rename(`Original β` = Estimate) %>%
  full_join(r1_comp_df %>%
              filter(Dataset != "Original, all items") %>%
              select(Dataset, Parameter, Estimate) %>%
              rename(`New β` = Estimate)) %>%
  mutate(`New β - Original β` = `New β` - `Original β`) %>%
  kable(digits = 2) %>%
  kable_styling() %>%
  collapse_rows(1:2)
```

```{r}
r1_bayes_comp_df %>%
  filter(Parameter != "Intercept") %>%
  ggplot(aes(x = Dataset, y = Estimate)) +
  facet_grid(~ Parameter) +
  geom_hline(yintercept = 0, lty = 2) +
  geom_pointrange(aes(ymin = Q2.5, ymax = Q97.5)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
  labs(title = "Comparing primary analysis across different datasets (Study 1)",
       subtitle = "Bayesian regression:\nbrm(spiritual experience ~ absorption * porosity + (1 | country/site/religion))",
       y = "β [95% Credible Interval]")
```

## Country as fixed effect

```{r}
rr2 <- lm(spev_recoded_std ~ pv_score_std * abs_score_std * country, d1r)
summary(rr2)
```

```{r}
piecewiseSEM::rsquared(rr2)
```

```{r}
regtab_fun(rr2, por_var = "pv_score_std", por_name = "Porosity Vignettes") %>% 
  regtab_style_fun(row_emph = 2:3)
```

