---
title: "Study 2"
subtitle: "Luhrmann, Weisman, et al."
output: 
  html_notebook:
    theme: flatly
    toc: true
    toc_float: true
---

In this notebook, we analyze Study 2: Pen-and-paper surveys with undergraduates.

```{r}
source("../../scripts_general/dependencies.R")
source("../../scripts_general/custom_funs.R")
source("../../scripts_general/var_recode_contrast.R")
source("../../scripts_general/data_load.R")
```

```{r}
# show contrasts
contrasts(d2_byquestion$country)
contrasts(d2$country)
```


# Demographics

```{r}
# all participants included in dataset
d2 %>% distinct(subj) %>% count()
```

```{r}
# participants missing absorption score
d2 %>% 
  filter(is.na(abs_score)) %>% 
  distinct(as.character(subj)) %>%
  count()

# participants missing daily spiritual experiences score
d2 %>% 
  filter(is.na(dse_score)) %>% 
  distinct(as.character(subj)) %>% 
  count()

# participants missing spiritual events score
d2 %>% 
  filter(is.na(spev_score)) %>% 
  distinct(as.character(subj)) %>% 
  count()

# participants with complete data for primary analysis
d2 %>% 
  filter(!is.na(abs_score),
         !is.na(dse_score),
         !is.na(spev_score)) %>% 
  distinct(as.character(subj)) %>% 
  count()
```

```{r}
# d2_demo <- d2_byquestion %>%
#   select(subj, country, starts_with("demo_"))
# 
# write_csv(d2_demo, "../data/d2_demo.csv")
```

```{r}
d2_demo <- read_csv("../data/d2_demo.csv") %>%
  mutate(male = ifelse(grepl("male", tolower(demo_sex)) &
                         !grepl("female", tolower(demo_sex)), 1, 0),
         female = ifelse(grepl("female", tolower(demo_sex)), 1, 0),
         subject_age = ifelse(demo_age > 120, NA_real_, demo_age),
         # demo_affr already formatted as 0 = cannot afford, 1 = can afford
         # demo_ses recoded so that -2 = much poorer, +2 = much richer
         demo_ses = demo_ses - 3,
         # demo_howr recoded so that -2 = strongly disagree, +2 = strongly agree
         demo_howr = demo_howr - 3)
```

```{r}
d2_demo %>%
  group_by(country) %>%
  summarise(n = n(),
            age_range = paste0(min(subject_age, na.rm = T), "-",
                               max(subject_age, na.rm = T)),
            mean_age = mean(subject_age, na.rm = T),
            percent_male = mean(male, na.rm = T),
            percent_female = mean(female, na.rm = T),
            percent_affr = mean(demo_affr, na.rm = T),
            mean_ses = mean(demo_ses, na.rm = T),
            mean_howr = mean(demo_howr, na.rm = T)) %>%
  ungroup() %>%
  # mutate_at(vars(starts_with("mean_")), funs(format(round(., 2), nsmall = 2))) %>%
  mutate_at(vars(starts_with("percent_")),
            funs(paste0(round(. * 100), "%"))) %>%
  rename(Country = country,
         `Age range` = age_range, `Mean age` = mean_age,
         `% male` = percent_male, `% female` = percent_female,
         `% can afford` = percent_affr,
         `Mean SES` = mean_ses,
         `Mean religiosity` = mean_howr) %>%
  kable(digits = 2, align = c(rep("l", 3), rep("r", 4))) %>%
  kable_styling(font_size = 16) # %>%
  # collapse_rows(1:3)
```


# Predicting Spiritual Experiences

```{r}
d2_long <- d2 %>%
  select(country, subj, abs_score_std, dse_score_std, spev_score_std) %>%
  gather(spirit_scale, spirit_score_std, 
         c(dse_score_std, spev_score_std)) %>%
  mutate(spirit_scale = factor(spirit_scale, 
                               levels = c("dse_score_std", "spev_score_std")))

contrasts(d2_long$country) <- contrasts_country; contrasts(d2_long$country)
contrasts(d2_long$spirit_scale) <- cbind("_spev" = c(-1, 1)); contrasts(d2_long$spirit_scale)
```

## Attempting to fit more complex random effects structures

```{r}
# more complex random effects structures: NOT REPORTED
# note: never looking for intercepts (random or fixed) by scale, because standardized
r1a <- lmer(spirit_score_std ~ 1 + abs_score_std +
              (1 | country/subj) +
              (0 + abs_score_std | country) +
              (0 + abs_score_std | spirit_scale),
            data = d2_long) # singular

r1b <- lmer(spirit_score_std ~ 1 + abs_score_std +
              (1 | country/subj) +
              (0 + abs_score_std | country),
            data = d2_long) # singular

r1c <- lmer(spirit_score_std ~ 1 + abs_score_std +
              (1 | country/subj) +
              (0 + abs_score_std | spirit_scale),
            data = d2_long) # overparameterized: only 1 df for testing main effect of abs_score

r1d <- lmer(spirit_score_std ~ abs_score_std + 
              (0 + abs_score_std | country) +
              (0 + abs_score_std | spirit_scale),
            data = d2_long) # fine, but doesn't reflect repeated measures design

r1e <- lmer(spirit_score_std ~ 1 + abs_score_std +
              (1 + abs_score_std | country), # singular
            # (1 + abs_score_std || country), # failed to converge
            data = d2_long) # singular

r1f <- lmer(spirit_score_std ~ 1 + abs_score_std +
              (1 | country/subj),
            data = d2_long) # fine, but doesn't account for two scales

r1g <- lmer(spirit_score_std ~ 1 + abs_score_std +
              (0 + abs_score_std | spirit_scale),
            data = d2_long) # overparameterized: only 1 df for testing main effect of abs_score

r1h <- lmer(spirit_score_std ~ 1 + abs_score_std +
              (1 + abs_score_std | country) + (1 | subj),
            data = d2_long) # singular
```

```{r}
r1i_dse <- lmer(dse_score_std ~ abs_score_std +
                  (1 + abs_score_std | country), d2) # singular

r1i_spev <- lmer(spev_score_std ~ abs_score_std +
                   (1 + abs_score_std | country), d2) # singular
```



## Primary analysis

### Daily Spiritual Experiences

```{r}
r1_dse <- lmer(dse_score_std ~ abs_score_std + 
                 (1 + abs_score_std || country), d2)
summary(r1_dse)
```

```{r}
rsquared(r1_dse)
```

```{r}
regtab_fun(r1_dse) %>% regtab_style_fun(row_emph = 2)
```

```{r}
regtab_ran_fun(r1_dse) %>% regtab_style_fun()
```

### Spiritual Events

```{r}
r1_spev <- lmer(spev_score_std ~ abs_score_std + 
                  (1 + abs_score_std || country), d2)
summary(r1_spev)
```

```{r}
rsquared(r1_spev)
```

```{r}
regtab_fun(r1_spev) %>% regtab_style_fun(row_emph = 2)
```

```{r}
regtab_ran_fun(r1_spev) %>% regtab_style_fun()
```

## Bayesian regression

### Daily Spiritual Experiences

```{r}
# r1_dse_bayes <- brm(dse_score_std ~ abs_score_std +
#                       (1 + abs_score_std || country), d2,
#                     control = list(adapt_delta = 0.99),
#                     seed = 1234, cores = 4, chains = 4)
# saveRDS(r1_dse_bayes, "./models/r1_dse_bayes.RDS")

r1_dse_bayes <- readRDS("./models/r1_dse_bayes.RDS")

summary(r1_dse_bayes)
```

```{r}
bayes_R2(r1_dse_bayes)
```

```{r}
regtab_fun(r1_dse_bayes) %>% regtab_style_fun(row_emph = 2)
```

```{r}
regtab_ran_fun(r1_dse_bayes) %>% regtab_style_fun()
```

### Spiritual Events

```{r}
# r1_spev_bayes <- brm(spev_score_std ~ abs_score_std +
#                       (1 + abs_score_std || country), d2,
#                     control = list(adapt_delta = 0.99),
#                     seed = 1234, cores = 4, chains = 4)
# saveRDS(r1_spev_bayes, "./models/r1_spev_bayes.RDS")

r1_spev_bayes <- readRDS("./models/r1_spev_bayes.RDS")

summary(r1_spev_bayes)
```

```{r}
bayes_R2(r1_spev_bayes)
```

```{r}
regtab_fun(r1_spev_bayes) %>% regtab_style_fun(row_emph = 2)
```

```{r}
regtab_ran_fun(r1_spev_bayes) %>% regtab_style_fun()
```

## Country as fixed effect

### Daily Spiritual Experiences

```{r}
r2_dse <- lm(dse_score_std ~ abs_score_std * country, d2)
summary(r2_dse)
```

```{r}
rsquared(r2_dse)
```

```{r}
regtab_fun(r2_dse) %>% regtab_style_fun(row_emph = 2)
```


### Spiritual Events

```{r}
r2_spev <- lm(spev_score_std ~ abs_score_std * country, d2)
summary(r2_spev)
```

```{r}
rsquared(r2_spev)
```

```{r}
regtab_fun(r2_spev) %>% regtab_style_fun(row_emph = 2)
```


